Learning Discrete Bayesian Networks from Continuous Data

### 2017-05-26 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
minor change

\jairheading{X}{XXXX}{XXX}{MM/YY}{MM/YY}
\ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
{Chen, Wheeler, \& Kochenderfer}
\firstpageno{25}

@@

\author{\name Yi-Chun Chen \email yichunc0419@alumni.stanford.edu \\
	\addr Institute of Computational and Mathematical Engineering, Stanford University,\\
	Stanford, CA  94035 USA
	\AND
	\name Tim A. Wheeler \email wheelert@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA
	\AND
	\name Mykel J. Kochenderfer \email mykel@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA}
%\authorrunning{Short form of author list} % if too long for running head

@@

\section{Multi-Variable Discretization}
\label{sec:multi_var}

@@

The global minimum of Equation~\ref{eqn:MDL} can be found using dynamic programming.
For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
Hence, if ${\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}}$ is an MDL optimal discretization policy with $k$ intervals, then ${\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}}$ is an MDL optimal discretization policy for the corresponding subproblem with $k-1$ intervals.
This procedure takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
All variables are defined in Section \ref{subsec:algo}.
Therefore, the runtime of the proposed method in this paper is less than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
For faster methods of MDL discretization with suboptimal results, see \citet{Friedman_1996}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix A}
\label{sec:appendixA}

@@

\section*{Appendix B}
\label{sec:appendixB}

@@

\subsection*{Auto MPG with Comparable MDL Performance}
The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
The network is structured more favorably with regards to discretization than the network in Figure~\ref{fig:auto_graph_1}, as the discretization policies were simultaneously learned with the network structure, resulting in higher data likelihood.
Many edges appear in both discretization results and are bolded in Table~\ref{table:auto_disc_table_3}.

@@

\subsection*{Reproducing MDL Results from the Literature}

>>>>

\jairheading{59}{2017}{XXX}{10/16}{05/17}
\ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
{Chen, Wheeler, \& Kochenderfer}
\firstpageno{25}

@@

\author{\name Yi-Chun Chen \email yichunc0419@alumni.stanford.edu \\
	\addr Institute of Computational and Mathematical Engineering,\\
	Stanford University, Stanford, CA  94035 USA
	\AND
	\name Tim A. Wheeler \email wheelert@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA
	\AND
	\name Mykel J. Kochenderfer \email mykel@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA}
%\authorrunning{Short form of author list} % if too long for running head

@@

\section{Multi-variable Discretization}
\label{sec:multi_var}

@@

The global minimum of Equation~\ref{eqn:MDL} can be found using dynamic programming.
For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
Hence, if ${\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}}$ is an MDL optimal discretization policy with $k$ intervals, then ${\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}}$ is an MDL optimal discretization policy for the corresponding subproblem with $k-1$ intervals.
This procedure takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
All variables are defined in Section \ref{subsec:algo}.
Therefore, the runtime of the proposed method in this paper is less than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
For faster methods of MDL discretization with suboptimal results also, see \citet{Friedman_1996}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix A.}
\label{sec:appendixA}

@@

\section*{Appendix B.}
\label{sec:appendixB}

@@

\subsection*{B.1 Auto MPG with Comparable MDL Performance}
The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
The network is structured more favorably with regards to discretization than the network in Figure~\ref{fig:auto_graph_1}, as the discretization policies were simultaneously learned with the network structure, resulting in higher data likelihood.
Many edges appear in both discretization results and are bolded in Table~\ref{table:auto_disc_table_3}.

@@

\subsection*{B.2 Reproducing MDL Results from the Literature}
